---
title: "Profiling ggplot2 - highlighted results"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(printr)

descriptions <- read_csv("plot_descriptions.csv")
rgd_timing <- read_csv("results/ggProfile_rgd_Darwin_quartz_2018-06-14.csv")
pdf_timing <- read_csv("results/ggProfile_pdf_Darwin_quartz_2018-06-14.csv")

date <- "2018-06-20"
pngs <- list.files("results/", pattern = paste0("png.*",date), full.names = T)
png_timing <- purrr::map_df(pngs, read_csv) %>%
  mutate(
    device = parse_factor(rep(c("cairo", "CairoPNG", "quartz", "Xlib", "win"), each = 101),
      levels = c("cairo", "quartz", "Xlib", "CairoPNG", "win")
    ),
    step = parse_factor(step, c("construct", "build", "render", "draw", "TOTAL"), ordered = TRUE),
    plot_type = parse_factor(plot_type, levels = rev(unique(plot_type)))
  )
```

# Notable results
- The addition of a loess smoother is an outlier, increasing the time to plot >25sec. 
This is likely a GAM issue, not caused by the simple addition of a 3rd layer in ggplot. 
Adding a second layer is no slower than simply plotting the 50K scatter plot. 
*Each of the following plots omit this plot for this reason*.
- Surprisingly, one large sf_polygon is slower to plot than 100 small sf_polygons with geom_sf
- Heavy facetting increases processing time of build, render, and draw steps.
- "Xlib" throws repeated warning: `In grid.Call.graphics(C_path, x$x, x$y, index, switch(x$rule,  ... :
  Path drawing not available for this device` and fails to draw `geom_sf` and `geom_polygon` plots correctly. 
  Affecting those measurements accordingly.

*For more verbose descriptions of the plots called, see description table at bottom of this file, 
or the plot calls in `ggprofile.R`*

## Graphics Device matters

### PNG

```{r, echo = F}
png_timing %>%
  filter(plot_type != "lyr3", plot_type == "BaseR" | step != "TOTAL") %>%
  ggplot(., aes(x = plot_type, y = elapsed, fill = step)) +
  geom_bar(stat = "identity", position = position_stack(reverse = T)) +
  facet_grid(. ~ device) + coord_flip() +
  scale_fill_viridis_d("Step", direction = -1) +
  labs(
    title = "Elapsed time by plotting step - PNG",
    x = "Plot", y = "Elapsed (secs)",
    subtitle = "Note: Plots were run in order from top to bottom, i.e. BaseR to sf_one", 
    caption = paste("Data collected on", date)
  ) + theme(legend.position = "bottom")
```

### PDF Quartz
```{r, echo = F}
pdf_timing %>%
  filter(plot_type != "lyr3", plot_type == "BaseR" | step != "TOTAL") %>%
  ggplot(., aes(
    x = parse_factor(plot_type, levels = rev(unique(plot_type))),
    y = elapsed,
    fill = parse_factor(step, c("construct", "build", "render", "draw", "TOTAL"),
      ordered = TRUE
    )
  )) +
  coord_flip() +
  geom_bar(stat = "identity", position = position_stack(reverse = T)) +
  scale_fill_viridis_d("Step", direction = -1) +
  labs(
    title = "Elapsed time by plotting step - PDF driver",
    x = "Plot", y = "Elapsed (secs)",
    subtitle = "Note: Plots were run in order from top to bottom, i.e. BaseR to sf_one"
  )
```

### RStudio GD
- Even with the addition of a `grid.new()` call in `tidy_benchmark`, 
Rstudio GD seems to drag and affect the estimates of construct when combined with `map`
- This `construct` inflation does not happen if you run each `tidy_benchplot` 
call individually and as such it's likely actually measuring the rgd doing its drawing from 
the previous plot. 

```{r, include = F}
mean_rgd <- rgd_timing %>%
  group_by(step, plot_type) %>%
  mutate(mean = mean(elapsed), driver = "RGD")
mean_pdf <- pdf_timing %>%
  group_by(step, plot_type) %>%
  mutate(mean = mean(elapsed), driver = "PDF")
bind_rows(mean_rgd, mean_pdf) %>%
  group_by(driver) %>%
  filter(step == "draw") %>%
  summarise(mean_draw = mean(elapsed))
```

```{r, echo = F}
rgd_timing %>%
  filter(plot_type != "lyr3", plot_type == "BaseR" | step != "TOTAL") %>%
  ggplot(., aes(
    x = parse_factor(plot_type, levels = rev(unique(plot_type))), y = elapsed,
    fill = parse_factor(step, c("construct", "build", "render", "draw", "TOTAL"),
      ordered = TRUE
    )
  )) + coord_flip() +
  geom_bar(stat = "identity", position = position_stack(reverse = T)) +
  scale_fill_viridis_d("Step", direction = -1) +
  labs(
    title = "Elapsed time by plotting step - RStudio GD",
    x = "Plot", y = "Elapsed (secs)",
    subtitle = "Note: Plots were run in order from top to bottom, i.e. BaseR to sf_one"
  )
```

### Plots Tested 

```{r, echo = F}
descriptions
```


