---
title: "Profiling ggplot2 - highlighted results"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(printr)

rgd_timing <- read_csv("results/ggProfile_Darwin_quartz_2018-06-14_RstudioGD.csv")
pdf_timing <- read_csv("results/ggProfile_Darwin_quartz_2018-06-14.csv")
descriptions <- read_csv("plot_descriptions.csv")
```

## Notable results
- Base scatter of diamonds is about 6.25 times faster than ggplot2. 
- The addition of a loess smoother is an outlier, increasing the time to plot >25sec. 
This is likely a GAM issue, not caused by the simple addition of a 3rd layer in ggplot. 
Adding a second layer is no slower than simply plotting the 50K scatter plot
- Surprisingly, one large sf_polygon is slower to plot than 100 small sf_polygons with geom_sf
- Heavy facetting has increases processing time of build, render, and draw steps


```{r, echo = F}
pdf_timing %>%
  filter(plot_type != "lyr3", plot_type == "BaseR" | step != "TOTAL") %>%
  ggplot(., aes(
    x = plot_type, y = elapsed,
    fill = parse_factor(step, c("TOTAL", "draw", "render", "build", "construct"))
  )) +
  geom_bar(stat = "identity") + scale_fill_viridis_d("Step") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  xlab("Plot") + ylab("Elapsed (secs)") +
  ggtitle("Elapsed time by plotting step - PDF driver")
```

### Plots Tested 

```{r, echo = F}
descriptions
```

### Driver matters 
- Even with the addition of a `grid.new()` call in `tidy_benchmark`, 
Rstudio GD seems to drag and affect the estimates of construct when combined with `map`
- This `construct` inflation does not happen if you run each `tidy_benchplot` call individually.
- Addionally draw times for the RStudio GD, take and average of 5.66 times longer then
calling the pdf driver instead. 

```{r}
mean_rgd <- rgd_timing %>%
  group_by(step, plot_type) %>%
  mutate(mean = mean(elapsed), driver = "RGD")
mean_pdf <- pdf_timing %>%
  group_by(step, plot_type) %>%
  mutate(mean = mean(elapsed), driver = "PDF")
bind_rows(mean_rgd, mean_pdf) %>%
  group_by(driver) %>%
  filter(step == "draw") %>%
  summarise(mean_draw = mean(elapsed))
```

```{r, echo=F}
rgd_timing %>%
  filter(plot_type != "lyr3", plot_type == "BaseR" | step != "TOTAL") %>%
  ggplot(., aes(
    x = plot_type, y = elapsed,
    fill = parse_factor(step, c("TOTAL", "draw", "render", "build", "construct"))
  )) +
  geom_bar(stat = "identity") + scale_fill_viridis_d("Step") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  xlab("Plot") + ylab("Elapsed (secs)") +
  ggtitle("Elapsed time by plotting step - PDF driver")
```